The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-11-30 donde.tex
submissions

\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

>>>>

\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback. Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the results.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}
